---
title: "William Pearman <br> Curriculum vitae (summary)"
output:
  pagedown::html_paged:
    css: ["css/bootstrap-5.2.1.min.css", "css/two-col-cv.css"]
    number_sections: false
knit: pagedown::chrome_print
params:
  n_awards: 6
  n_pubs: 8
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
library(glue)
library(fontawesome)
library(knitr)
source("_common.R")
meta <- load_meta()

year_table <- function(d, year_col, text_col) {
  d |>
    transmute(Year = .data[[year_col]], What = .data[[text_col]]) |>
    kable(col.names = c("", ""), escape = FALSE)
}
```

::: {.row}

:::::: {.col-8 .summary}

# Research summary

I am a broadly trained molecular and microbial ecologist specialising in population genomics and microbial ecology, developing eco-evolutionary simulations of host-microbe (holobiont) relationships tested against observational and experimental data.

::::::

:::::: {.col-4}

# Contact {.box}

::::::::: {.info-box}

| Center | Left |
|:------:|:-----|
| `r fa("map-marker-alt")` | `r meta$employer`, `r positions_tibble()$location[1]` |
| `r fa("envelope")` | `r meta$email` |
| `r fa("orcid")` | [`r meta$orcid`](`r meta$orcid_url`) |
| `r fa("github")` | [`r url_handle(meta$github)`](`r meta$github`) |

:::::::::

::::::

:::

::: {.row}

:::::: {.col-6 .left}

# Education

```{r}
education_tibble() |>
  mutate(what = glue("<span class='cv-entry-title'>{degree}</span>, {institution}, {location}")) |>
  year_table("year", "what")
```

::::::

:::::: {.col-6 .right}

# Awards and honours

```{r}
distinctions_tibble(category = "award") |>
  arrange(desc(year)) |>
  head(params$n_awards) |>
  year_table("year", "description")
```

::::::

:::

::: {.row}

:::::: {.col-12}

# Selected Publications

```{r}
#| results: asis
cat(render_cv_publications(top_n = params$n_pubs, rank_by = "cites"))
```

::::::

:::
