---
title: "William Pearman <br> Curriculum vitae (summary)"
output:
  pagedown::html_paged:
    css: ["css/bootstrap-5.2.1.min.css", "css/two-col-cv.css"]
    number_sections: false
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
library(glue)
library(fontawesome)
library(knitr)
source("_common.R")
meta <- load_meta()
view <- "onepage_cv"

year_table <- function(d, year_col, text_col) {
  d |>
    transmute(Year = .data[[year_col]], What = .data[[text_col]]) |>
    kable(col.names = c("", ""), escape = FALSE)
}

# Section content is entirely driven by content/cv_entries.csv's
# show_onepage_cv column (and content/pubs.csv's show_onepage_cv) -- to
# change what appears here, flip those flags rather than editing this file.
```

::: {.row}

:::::: {.col-7 .summary}

# Research summary

I am a broadly trained molecular and microbial ecologist specialising in population genomics and microbial ecology, developing eco-evolutionary simulations of host-microbe (holobiont) relationships tested against observational and experimental data.

::::::

:::::: {.col-5}

# Contact {.box}

::::::::: {.info-box}

| Center | Left |
|:------:|:-----|
| `r fa("map-marker-alt")` | `r meta$employer`, `r positions_tibble()$location[1]` |
| `r fa("envelope")` | `r meta$email` |
| `r fa("orcid")` | [`r meta$orcid`](`r meta$orcid_url`) |
| `r fa("github")` | [`r url_handle(meta$github)`](`r meta$github`) |

:::::::::

::::::

:::

::: {.row}

:::::: {.col-6 .left}

# Education

```{r}
cv_entries("education", view) |>
  mutate(what = glue("<span class='cv-entry-title'>{title}</span>, {where}, {location}")) |>
  year_table("year", "what")
```

::::::

:::::: {.col-6 .right}

# Awards and honours

```{r}
cv_entries("award", view) |>
  year_table("year", "title")
```

::::::

:::

::: {.row}

:::::: {.col-12}

# Selected major grants

```{r}
cv_entries("grant", view) |>
  year_table("year", "title")
```

::::::

:::

::: {.row}

:::::: {.col-12}

# Selected Publications

```{r}
#| results: asis
cat(render_cv_publications(view))
```

::::::

:::
