---
title: "Recipes"
description: "Recipes I make, with a servings calculator for each."
include-in-header:
  text: |
    <script>
    // Quarto's OJS runtime auto-generates a shinyInput() call for every
    // "viewof" cell as a bridge for Shiny-interactive documents. This page
    // has no Shiny backend, so without a stub that call throws a
    // ReferenceError deep inside the OJS module's evaluation, which was
    // silently blocking every single cell on the page (not just the
    // password-gated ones) from ever finishing "waiting for module
    // import". A no-op stub here, defined before the OJS runtime script
    // runs, fixes it.
    window.shinyInput = window.shinyInput || function () {};
    </script>
---

Drag the slider on any recipe to scale the ingredient amounts up or down.

Recipes from other people's own kitchens or family archives are shown in
full. Recipes from commercial publications aren't reproduced here out of
respect for the original publishers -- a link to the source is always
given instead. Those ones are password protected purely so I can still
pull them up easily myself when I'm cooking.

```{r setup, include=FALSE}
library(yaml)
library(jsonlite)
library(openssl)
recipes <- yaml::read_yaml(here::here("content", "recipes.yml"))
is_protected <- function(r) isTRUE(r$protected)
any_protected <- any(vapply(recipes, is_protected, logical(1)))

# PBKDF2-HMAC-SHA256 (RFC 8018), implemented by hand since neither
# base R nor the openssl/digest packages expose it directly. Verified
# byte-for-byte against Python's hashlib.pbkdf2_hmac for both a single
# iteration and 4096 iterations before relying on it here. Needs to be
# bit-for-bit compatible with the browser's native
# crypto.subtle.deriveKey({name: "PBKDF2", ...}) -- see unlock_cells
# below, which derives the same key client-side from the same
# salt/iterations to decrypt what this function encrypts.
pbkdf2_hmac_sha256 <- function(password, salt, iterations, dklen = 32) {
  hlen <- 32
  n_blocks <- ceiling(dklen / hlen)
  out <- raw(0)
  for (i in seq_len(n_blocks)) {
    int_be <- as.raw(c((i %/% 16777216) %% 256, (i %/% 65536) %% 256, (i %/% 256) %% 256, i %% 256))
    u <- digest::hmac(key = password, object = c(salt, int_be), algo = "sha256", serialize = FALSE, raw = TRUE)
    t <- u
    if (iterations > 1) {
      for (j in 2:iterations) {
        u <- digest::hmac(key = password, object = u, algo = "sha256", serialize = FALSE, raw = TRUE)
        t <- as.raw(bitwXor(as.integer(t), as.integer(u)))
      }
    }
    out <- c(out, t)
  }
  out[seq_len(dklen)]
}

RECIPE_PBKDF2_ITERATIONS <- 250000

# The protected recipes are genuinely encrypted here, not just hidden
# behind a password *check* -- content/recipes.yml (source) and
# docs/protected_recipes.json (the file the unlock button fetches) both
# contain real recipe data, so encrypting the latter is what actually
# keeps it unreadable to anyone browsing the repo or the deployed site
# without the password (content/recipes.yml itself is still plaintext,
# see below). AES-256-CBC, key derived via PBKDF2-HMAC-SHA256 with a
# random salt and 250,000 iterations -- the same derivation the browser
# repeats client-side from the same salt to get the same key (see
# unlock_cells). CBC has no built-in authentication, so a wrong
# password just decrypts to garbage bytes rather than throwing outright;
# that's caught client-side because the garbage then fails to parse as
# JSON.
#
# The plaintext password itself is never written to this file, or
# anywhere else in the repo -- it's read locally at render time from
# .recipe_secret (gitignored). To change the password, edit that file
# and re-render.
encrypt_protected_data <- function(data, password) {
  salt <- openssl::rand_bytes(16)
  iv <- openssl::rand_bytes(16)
  key <- pbkdf2_hmac_sha256(charToRaw(password), salt, RECIPE_PBKDF2_ITERATIONS)
  plaintext <- charToRaw(jsonlite::toJSON(data, auto_unbox = TRUE))
  ciphertext <- openssl::aes_cbc_encrypt(plaintext, key = key, iv = iv)
  list(
    salt = openssl::base64_encode(salt),
    iv = openssl::base64_encode(iv),
    iterations = RECIPE_PBKDF2_ITERATIONS,
    ciphertext = openssl::base64_encode(ciphertext)
  )
}

source_line <- function(r) {
  if (is.null(r$source_url)) return("")
  label <- if (!is.null(r$source_name)) paste0("Recipe from [", r$source_name, "](", r$source_url, ")") else paste0("Recipe source: <", r$source_url, ">")
  paste0("*", label, "*\n\n")
}

# Public recipe: heading + OJS servings calculator, generated as raw
# markdown/OJS source text for cat()-ing in a results='asis' chunk --
# content/recipes.yml is the single source of truth for recipe content,
# this just re-derives the same block structure the old hand-written
# per-recipe OJS code used, with a unique variable prefix (slug) per
# recipe so they don't clash.
render_recipe <- function(r) {
  ingredients_json <- jsonlite::toJSON(r$ingredients, auto_unbox = TRUE)
  # slider must comfortably span the base serving count -- a fixed [1, 12]
  # range breaks any recipe whose base is above 12 (e.g. a 28-cookie batch)
  slider_max <- max(12, ceiling(r$base_servings * 2))
  paste0(
    "\n\n## ", r$name, "\n\n",
    source_line(r),
    "Base recipe serves **", r$base_servings, "**.\n\n",
    "```{ojs}\n//| echo: false\n",
    "viewof ", r$slug, "_servings = Inputs.range(\n",
    "  [1, ", slider_max, "], {value: ", r$base_servings, ", step: 1, label: \"Servings\"}\n",
    ")\n```\n\n",
    "```{ojs}\n//| echo: false\n",
    r$slug, "_base = ({\n",
    "  servings: ", r$base_servings, ",\n",
    "  ingredients: ", ingredients_json, "\n",
    "})\n```\n\n",
    "```{ojs}\n//| echo: false\n",
    r$slug, "_scaled = {\n",
    "  const ratio = ", r$slug, "_servings / ", r$slug, "_base.servings;\n",
    "  return ", r$slug, "_base.ingredients.map(i => ({\n",
    "    Ingredient: i.name,\n",
    "    Amount: Math.round(i.amount * ratio * 100) / 100,\n",
    "    Unit: i.unit\n",
    "  }));\n",
    "}\n```\n\n",
    "```{ojs}\n//| echo: false\n",
    "Inputs.table(", r$slug, "_scaled, {columns: [\"Ingredient\", \"Amount\", \"Unit\"]})\n",
    "```\n\n",
    r$instructions, "\n\n<br>\n\n"
  )
}

# Protected recipe: heading + always-visible source link, then a
# servings slider + ingredient table + instructions using the exact same
# Inputs.range()/Inputs.table() primitives as render_recipe() -- kept
# inert (label "Locked", empty table) until `recipe_unlocked` (defined
# once below) goes true, at which point it reads from
# docs/protected_recipes.json (fetched client-side, see unlock_cells).
#
# An earlier version built the unlocked UI by hand with html`...` and
# manual DOM/event-listener wiring in one big cell. That worked fine for
# a single protected recipe in isolation, but with multiple protected
# recipes on the same page (all depending on the same shared
# protected_recipe_data cell), only the first one's DOM update actually
# landed -- the rest stayed stuck displaying stale content even though
# their values had genuinely recomputed. Rebuilding it from the same
# small, proven Inputs.range()/Inputs.table() cells the public recipes
# already use (rather than one big custom cell) avoids that fan-out bug
# entirely.
render_locked_recipe <- function(r) {
  slider_max <- max(12, ceiling(r$base_servings * 2))
  slug <- r$slug
  paste0(
    "\n\n## ", r$name, "\n\n",
    source_line(r),
    "```{ojs}\n//| echo: false\n",
    "viewof ", slug, "_servings = Inputs.range(\n",
    "  [1, ", slider_max, "], {value: ", r$base_servings, ", step: 1, label: recipe_unlocked ? \"Servings\" : \"🔒 Locked\"}\n",
    ")\n```\n\n",
    "```{ojs}\n//| echo: false\n",
    slug, "_scaled = recipe_unlocked && protected_recipe_data\n",
    "  ? protected_recipe_data[\"", slug, "\"].ingredients.map(i => ({\n",
    "      Ingredient: i.name,\n",
    "      Amount: Math.round(i.amount * ", slug, "_servings / protected_recipe_data[\"", slug, "\"].base_servings * 100) / 100,\n",
    "      Unit: i.unit\n",
    "    }))\n",
    "  : []\n```\n\n",
    "```{ojs}\n//| echo: false\n",
    "Inputs.table(", slug, "_scaled, {columns: [\"Ingredient\", \"Amount\", \"Unit\"]})\n",
    "```\n\n",
    "```{ojs}\n//| echo: false\n",
    "md`${recipe_unlocked && protected_recipe_data ? protected_recipe_data[\"", slug, "\"].instructions : \"🔒 This recipe is password protected. Enter the password above to view it.\"}`\n",
    "```\n\n<br>\n\n"
  )
}

# Encrypted data for protected recipes only, written as a separate
# static file rather than embedded in this page's HTML. It's fetched
# and decrypted client-side only after a correct password is entered.
#
# 250,000 PBKDF2 iterations in pure R (no compiled implementation is
# readily available -- checked openssl, digest and sodium; none expose
# one) takes ~30 seconds. Paying that on *every* render, including ones
# that only touch a public recipe or an unrelated page, would make the
# whole site slow to iterate on. So this only re-encrypts when
# content/recipes.yml or .recipe_secret are newer than the last
# encrypted output -- editing a public recipe, or re-rendering anything
# else, reuses the existing docs/protected_recipes.json untouched.
protected_recipes_list <- Filter(is_protected, recipes)
if (length(protected_recipes_list) > 0) {
  secret_path <- here::here(".recipe_secret")
  if (!file.exists(secret_path)) {
    stop(
      "content/recipes.yml has protected recipes but .recipe_secret is missing.\n",
      "Create it at the project root with the unlock password on a single line ",
      "(gitignored, never committed) and re-render."
    )
  }
  out_path <- here::here("docs", "protected_recipes.json")
  recipes_yml_path <- here::here("content", "recipes.yml")
  needs_reencrypt <- !file.exists(out_path) ||
    file.info(recipes_yml_path)$mtime > file.info(out_path)$mtime ||
    file.info(secret_path)$mtime > file.info(out_path)$mtime

  if (needs_reencrypt) {
    recipe_password <- trimws(readLines(secret_path, warn = FALSE)[1])
    protected_data <- protected_recipes_list |>
      lapply(function(r) list(base_servings = r$base_servings, instructions = r$instructions, ingredients = r$ingredients)) |>
      setNames(vapply(protected_recipes_list, function(r) r$slug, character(1)))
    encrypted <- encrypt_protected_data(protected_data, recipe_password)
    jsonlite::write_json(encrypted, out_path, auto_unbox = TRUE)
  }
}

# `recipe_unlocked` and `protected_recipe_data` deliberately read
# sessionStorage rather than being reactively derived live from the
# password field. Quarto's OJS runtime turns out to have a scale-related
# bug: when a cell that's an upstream dependency of many other cells
# (here, ~20 across 5 protected recipes) changes value interactively
# (i.e. after the page has already loaded), most of those downstream
# cells silently never re-render even though their values genuinely
# recomputed (confirmed by inspecting the runtime's own promise state
# directly) -- only the first one or two do. The *initial* page load
# doesn't hit this bug -- all cells render fine on first evaluation,
# regardless of count. So instead of a live/typed password reactively
# unlocking things, a button does the actual decryption (see below) and,
# if it succeeds, caches the *decrypted* data in sessionStorage and
# reloads the page -- every cell then re-evaluates fresh from a clean
# load, with `recipe_unlocked`/`protected_recipe_data` already populated
# from the very first tick (a synchronous sessionStorage read, no fetch
# or decrypt needed post-reload), matching the same code path that's
# already proven reliable.
#
# The password input and unlock button are built in a single cell
# (rather than a separate `viewof recipe_password_input` cell that the
# button cell references) so the click handler can close over the input
# element directly, as a plain local JS variable, and read its *live*
# `.value` at click time. Referencing another cell's value from inside
# a nested async closure looked like it should work the same way -- OJS
# is supposed to resolve cross-cell references dynamically -- but it
# consistently read back the value from when the button cell first
# rendered rather than what was currently typed, so every click failed
# with "incorrect password" even when the password was right. Keeping
# everything in one cell with a real DOM reference sidesteps that
# entirely.
unlock_cells <- paste0(
  "```{ojs}\n//| echo: false\n",
  "viewof recipe_unlock_form = {\n",
  "  const input = html`<input type=\"password\" placeholder=\"Password for protected recipes\">`;\n",
  "  const btn = html`<button>Unlock</button>`;\n",
  "  const err = html`<span style=\"color:#b00020; margin-left:0.5em;\"></span>`;\n",
  "  const b64ToBytes = b64 => Uint8Array.from(atob(b64), c => c.charCodeAt(0));\n",
  "  const tryUnlock = async () => {\n",
  "    err.textContent = \"\";\n",
  "    try {\n",
  "      const enc = await fetch(\"protected_recipes.json\").then(r => r.json());\n",
  "      const passKey = await crypto.subtle.importKey(\n",
  "        \"raw\", new TextEncoder().encode(input.value), \"PBKDF2\", false, [\"deriveKey\"]\n",
  "      );\n",
  "      const key = await crypto.subtle.deriveKey(\n",
  "        {name: \"PBKDF2\", salt: b64ToBytes(enc.salt), iterations: enc.iterations, hash: \"SHA-256\"},\n",
  "        passKey, {name: \"AES-CBC\", length: 256}, false, [\"decrypt\"]\n",
  "      );\n",
  "      const plainBuf = await crypto.subtle.decrypt(\n",
  "        {name: \"AES-CBC\", iv: b64ToBytes(enc.iv)}, key, b64ToBytes(enc.ciphertext)\n",
  "      );\n",
  # AES-CBC has no built-in authentication, so a wrong password doesn't
  # reliably throw here -- it can decrypt to plausible-looking garbage.
  # JSON.parse()-ing that garbage is what actually catches a wrong
  # password in practice.
  "      const data = JSON.parse(new TextDecoder().decode(plainBuf));\n",
  "      sessionStorage.setItem(\"recipesUnlocked\", \"1\");\n",
  "      sessionStorage.setItem(\"recipesData\", JSON.stringify(data));\n",
  "      location.reload();\n",
  "    } catch (e) {\n",
  "      err.textContent = \"Incorrect password.\";\n",
  "    }\n",
  "  };\n",
  "  btn.onclick = tryUnlock;\n",
  "  input.addEventListener(\"keydown\", e => { if (e.key === \"Enter\") tryUnlock(); });\n",
  "  return html`<span>${input} ${btn}${err}</span>`;\n",
  "}\n```\n\n",
  "```{ojs}\n//| echo: false\n",
  'recipe_unlocked = sessionStorage.getItem("recipesUnlocked") === "1"\n',
  "```\n\n",
  "```{ojs}\n//| echo: false\n",
  # A plain synchronous sessionStorage read. The fan-out bug described
  # above is specifically about a cell's value changing *live* after
  # the page has already loaded; reading sessionStorage here happens
  # during the same initial-evaluation pass as every other cell on the
  # page (which is unaffected), not as a later reactive update, so it
  # doesn't hit that case.
  'protected_recipe_data = recipe_unlocked ? JSON.parse(sessionStorage.getItem("recipesData")) : null\n',
  "```\n\n"
)
```

```{r}
#| results: asis
#| echo: false
if (any_protected) cat(unlock_cells)
cat(paste(vapply(recipes, function(r) if (is_protected(r)) render_locked_recipe(r) else render_recipe(r), character(1)), collapse = "\n"))
```
