---
title: "Recipes"
description: "Recipes I make, with a servings calculator for each."
---

Drag the slider on any recipe to scale the ingredient amounts up or down.

```{r setup, include=FALSE}
library(yaml)
library(jsonlite)
recipes <- yaml::read_yaml(here::here("content", "recipes.yml"))

# Generates one recipe's heading + OJS servings calculator as raw
# markdown/OJS source text, for cat()-ing in a results='asis' chunk --
# content/recipes.yml is the single source of truth for recipe content,
# this just re-derives the same block structure the old hand-written
# per-recipe OJS code used, with a unique variable prefix (slug) per
# recipe so they don't clash.
render_recipe <- function(r) {
  ingredients_json <- jsonlite::toJSON(r$ingredients, auto_unbox = TRUE)
  # slider must comfortably span the base serving count -- a fixed [1, 12]
  # range breaks any recipe whose base is above 12 (e.g. a 28-cookie batch)
  slider_max <- max(12, ceiling(r$base_servings * 2))
  source_line <- if (!is.null(r$source_url)) {
    paste0("*Recipe", if (!is.null(r$source_name)) paste0(" from [", r$source_name, "](", r$source_url, ")") else paste0(" source: <", r$source_url, ">"), "*\n\n")
  } else ""
  paste0(
    "\n\n## ", r$name, "\n\n",
    source_line,
    "Base recipe serves **", r$base_servings, "**.\n\n",
    "```{ojs}\n//| echo: false\n",
    "viewof ", r$slug, "_servings = Inputs.range(\n",
    "  [1, ", slider_max, "], {value: ", r$base_servings, ", step: 1, label: \"Servings\"}\n",
    ")\n```\n\n",
    "```{ojs}\n//| echo: false\n",
    r$slug, "_base = ({\n",
    "  servings: ", r$base_servings, ",\n",
    "  ingredients: ", ingredients_json, "\n",
    "})\n```\n\n",
    "```{ojs}\n//| echo: false\n",
    r$slug, "_scaled = {\n",
    "  const ratio = ", r$slug, "_servings / ", r$slug, "_base.servings;\n",
    "  return ", r$slug, "_base.ingredients.map(i => ({\n",
    "    Ingredient: i.name,\n",
    "    Amount: Math.round(i.amount * ratio * 100) / 100,\n",
    "    Unit: i.unit\n",
    "  }));\n",
    "}\n```\n\n",
    "```{ojs}\n//| echo: false\n",
    "Inputs.table(", r$slug, "_scaled, {columns: [\"Ingredient\", \"Amount\", \"Unit\"]})\n",
    "```\n\n",
    r$instructions, "\n\n<br>\n\n"
  )
}
```

```{r}
#| results: asis
#| echo: false
cat(paste(vapply(recipes, render_recipe, character(1)), collapse = "\n"))
```
