---
title: "Recipes"
description: "Recipes I make, with a servings calculator for each."
include-in-header:
  text: |
    <script>
    // Quarto's OJS runtime auto-generates a shinyInput() call for every
    // "viewof" cell as a bridge for Shiny-interactive documents. This page
    // has no Shiny backend, so without a stub that call throws a
    // ReferenceError deep inside the OJS module's evaluation, which was
    // silently blocking every single cell on the page (not just the
    // password-gated ones) from ever finishing "waiting for module
    // import". A no-op stub here, defined before the OJS runtime script
    // runs, fixes it.
    window.shinyInput = window.shinyInput || function () {};
    </script>
---

Drag the slider on any recipe to scale the ingredient amounts up or down.

Recipes from other people's own kitchens or family archives are shown in
full. Recipes from commercial publications aren't reproduced here out of
respect for the original publishers -- a link to the source is always
given instead. Those ones are password protected purely so I can still
pull them up easily myself when I'm cooking.

```{r setup, include=FALSE}
library(yaml)
library(jsonlite)
recipes <- yaml::read_yaml(here::here("content", "recipes.yml"))
is_protected <- function(r) isTRUE(r$protected)
any_protected <- any(vapply(recipes, is_protected, logical(1)))

# Only the SHA-256 hash of the unlock password is embedded in the page --
# never the plaintext -- and it's checked client-side with the browser's
# own Web Crypto API. This is a casual deterrent, not real security: the
# protected recipes' data still ships as a plain JSON file in docs/ (see
# below) that anyone who finds the URL could fetch directly. That's an
# accepted tradeoff for a static GitHub Pages site with no backend.
#
# This is the *hash* only -- the plaintext password is never written to
# this file (or anywhere else in the repo). To change the password,
# compute a new hash with:
#   Rscript -e 'digest::digest("new password here", algo="sha256", serialize=FALSE)'
# and paste the result below.
RECIPE_LOCK_HASH <- "acf193e8bedf873524444fd11578e7e90c9874845628da26d66c76ceb2b108cb"

source_line <- function(r) {
  if (is.null(r$source_url)) return("")
  label <- if (!is.null(r$source_name)) paste0("Recipe from [", r$source_name, "](", r$source_url, ")") else paste0("Recipe source: <", r$source_url, ">")
  paste0("*", label, "*\n\n")
}

# Public recipe: heading + OJS servings calculator, generated as raw
# markdown/OJS source text for cat()-ing in a results='asis' chunk --
# content/recipes.yml is the single source of truth for recipe content,
# this just re-derives the same block structure the old hand-written
# per-recipe OJS code used, with a unique variable prefix (slug) per
# recipe so they don't clash.
render_recipe <- function(r) {
  ingredients_json <- jsonlite::toJSON(r$ingredients, auto_unbox = TRUE)
  # slider must comfortably span the base serving count -- a fixed [1, 12]
  # range breaks any recipe whose base is above 12 (e.g. a 28-cookie batch)
  slider_max <- max(12, ceiling(r$base_servings * 2))
  paste0(
    "\n\n## ", r$name, "\n\n",
    source_line(r),
    "Base recipe serves **", r$base_servings, "**.\n\n",
    "```{ojs}\n//| echo: false\n",
    "viewof ", r$slug, "_servings = Inputs.range(\n",
    "  [1, ", slider_max, "], {value: ", r$base_servings, ", step: 1, label: \"Servings\"}\n",
    ")\n```\n\n",
    "```{ojs}\n//| echo: false\n",
    r$slug, "_base = ({\n",
    "  servings: ", r$base_servings, ",\n",
    "  ingredients: ", ingredients_json, "\n",
    "})\n```\n\n",
    "```{ojs}\n//| echo: false\n",
    r$slug, "_scaled = {\n",
    "  const ratio = ", r$slug, "_servings / ", r$slug, "_base.servings;\n",
    "  return ", r$slug, "_base.ingredients.map(i => ({\n",
    "    Ingredient: i.name,\n",
    "    Amount: Math.round(i.amount * ratio * 100) / 100,\n",
    "    Unit: i.unit\n",
    "  }));\n",
    "}\n```\n\n",
    "```{ojs}\n//| echo: false\n",
    "Inputs.table(", r$slug, "_scaled, {columns: [\"Ingredient\", \"Amount\", \"Unit\"]})\n",
    "```\n\n",
    r$instructions, "\n\n<br>\n\n"
  )
}

# Protected recipe: heading + always-visible source link, then a
# servings slider + ingredient table + instructions using the exact same
# Inputs.range()/Inputs.table() primitives as render_recipe() -- kept
# inert (label "Locked", empty table) until `recipe_unlocked` (defined
# once below) goes true, at which point it reads from
# docs/protected_recipes.json (fetched client-side, see unlock_cells).
#
# An earlier version built the unlocked UI by hand with html`...` and
# manual DOM/event-listener wiring in one big cell. That worked fine for
# a single protected recipe in isolation, but with multiple protected
# recipes on the same page (all depending on the same shared
# protected_recipe_data cell), only the first one's DOM update actually
# landed -- the rest stayed stuck displaying stale content even though
# their values had genuinely recomputed. Rebuilding it from the same
# small, proven Inputs.range()/Inputs.table() cells the public recipes
# already use (rather than one big custom cell) avoids that fan-out bug
# entirely.
render_locked_recipe <- function(r) {
  slider_max <- max(12, ceiling(r$base_servings * 2))
  slug <- r$slug
  paste0(
    "\n\n## ", r$name, "\n\n",
    source_line(r),
    "```{ojs}\n//| echo: false\n",
    "viewof ", slug, "_servings = Inputs.range(\n",
    "  [1, ", slider_max, "], {value: ", r$base_servings, ", step: 1, label: recipe_unlocked ? \"Servings\" : \"🔒 Locked\"}\n",
    ")\n```\n\n",
    "```{ojs}\n//| echo: false\n",
    slug, "_scaled = recipe_unlocked && protected_recipe_data\n",
    "  ? protected_recipe_data[\"", slug, "\"].ingredients.map(i => ({\n",
    "      Ingredient: i.name,\n",
    "      Amount: Math.round(i.amount * ", slug, "_servings / protected_recipe_data[\"", slug, "\"].base_servings * 100) / 100,\n",
    "      Unit: i.unit\n",
    "    }))\n",
    "  : []\n```\n\n",
    "```{ojs}\n//| echo: false\n",
    "Inputs.table(", slug, "_scaled, {columns: [\"Ingredient\", \"Amount\", \"Unit\"]})\n",
    "```\n\n",
    "```{ojs}\n//| echo: false\n",
    "md`${recipe_unlocked && protected_recipe_data ? protected_recipe_data[\"", slug, "\"].instructions : \"🔒 This recipe is password protected. Enter the password above to view it.\"}`\n",
    "```\n\n<br>\n\n"
  )
}

# Data for protected recipes only, written as a separate static file
# rather than embedded in this page's HTML -- fetched client-side only
# after the password check passes, so a plain view-source of recipes.html
# won't reveal it.
protected_recipes_list <- Filter(is_protected, recipes)
protected_data <- protected_recipes_list |>
  lapply(function(r) list(base_servings = r$base_servings, instructions = r$instructions, ingredients = r$ingredients)) |>
  setNames(vapply(protected_recipes_list, function(r) r$slug, character(1)))
jsonlite::write_json(protected_data, here::here("docs", "protected_recipes.json"), auto_unbox = TRUE)

# `recipe_unlocked` deliberately reads sessionStorage rather than being
# reactively derived from the password field. Quarto's OJS runtime turns
# out to have a scale-related bug: when a cell that's an upstream
# dependency of many other cells (here, ~20 across 5 protected recipes)
# changes value interactively (i.e. after the page has already loaded),
# most of those downstream cells silently never re-render even though
# their values genuinely recomputed (confirmed by inspecting the
# runtime's own promise state directly) -- only the first one or two do.
# The *initial* page load doesn't hit this bug -- all cells render fine
# on first evaluation, regardless of count. So instead of a live/typed
# password reactively unlocking things, a button verifies the password
# and, if correct, stores that in sessionStorage and reloads the page --
# every cell then re-evaluates fresh from a clean load, with
# `recipe_unlocked` already true from the very first tick, matching the
# same code path that's already proven reliable.
unlock_cells <- paste0(
  "```{ojs}\n//| echo: false\n",
  'viewof recipe_password_input = html`<input type="password" placeholder="Password for protected recipes">`\n',
  "```\n\n",
  "```{ojs}\n//| echo: false\n",
  "viewof recipe_unlock_button = {\n",
  "  const btn = html`<button>Unlock</button>`;\n",
  "  const err = html`<span style=\"color:#b00020; margin-left:0.5em;\"></span>`;\n",
  "  btn.onclick = async () => {\n",
  "    const buf = await crypto.subtle.digest(\"SHA-256\", new TextEncoder().encode(recipe_password_input));\n",
  "    const hex = Array.from(new Uint8Array(buf)).map(b => b.toString(16).padStart(2, \"0\")).join(\"\");\n",
  "    if (hex === \"", RECIPE_LOCK_HASH, "\") {\n",
  "      sessionStorage.setItem(\"recipesUnlocked\", \"1\");\n",
  "      location.reload();\n",
  "    } else {\n",
  "      err.textContent = \"Incorrect password.\";\n",
  "    }\n",
  "  };\n",
  "  return html`<span>${btn}${err}</span>`;\n",
  "}\n```\n\n",
  "```{ojs}\n//| echo: false\n",
  'recipe_unlocked = sessionStorage.getItem("recipesUnlocked") === "1"\n',
  "```\n\n",
  "```{ojs}\n//| echo: false\n",
  'protected_recipe_data = recipe_unlocked ? await fetch("protected_recipes.json").then(r => r.json()) : null\n',
  "```\n\n"
)
```

```{r}
#| results: asis
#| echo: false
if (any_protected) cat(unlock_cells)
cat(paste(vapply(recipes, function(r) if (is_protected(r)) render_locked_recipe(r) else render_recipe(r), character(1)), collapse = "\n"))
```
